\documentclass[a4paper,twoside]{book}
\usepackage{graphicx}
\usepackage{url}
\usepackage{siunitx}
\usepackage{harvard}
% This is the chapter titled `Optical TEMPEST' in Ireneusz Kubiak's new book.
\begin{document}
\title{New Book}
\author{Joe Loughry}
\setcounter{chapter}{6} % This chapter will be Chapter 7 of the book.
\chapter{Optical TEMPEST}
Optical TEMPEST is

electromagnetic but in the optical spectrum; we consider that to include at
least infrared (wavelengths longer than \SI{700}{\nano\metre}) because of the
ubiquitousness of light emitting diode (LED) sources in that range and their
convenient invisibility to humans.

reiterate the Class I, II, III taxonomy

\section{History}
The U.S.\ National Security Agency (NSA) named TEMPEST, as far as we know. We
don't even know for sure that the word is not an acronym. It is believed to
be a code name, \textsc{Tempest}\footnote{Evidence for it is shaky but there
was supposedly another programme called \textsc{Teapot} dealing with
stimulated RF compromising emanations \cite[p.~539]{Anderson2008a} and
partially corroborated in December of 2013 by Edward Snowden (NSA ANT
catalogue).} but evidence in the open literature is scarce; the only clear
original source is one declassified document dating from 1972
\cite{NSAtempest2007}.
\subsection{Information Leakage}
\subsubsection{Electromagnetic}
Field telephones in WWI; {\it funkspiel} in WWII; electromechanical cypher
machines in West Berlin. (This topic is covered well elsewhere in the book.)
\subsection{TEMPEST}
The protection of information from remote eavesdropping; air gaps; control
zones; protected distribution systems (PDS)\footnote{Visibility, stories of
poison gas, flammable gas, pressure gauges---reference Anderson (2001).} The
inclusion of acoustic but overlooking of optical, with the exception of
shoulder surfing. Contextual blindness?
\subsection{Optical}
\section{Physical Principles}
Photons, energy, generation atmospheric absorption. Recent development of
high efficiency LEDs (and the unexpected effect that had on reversing LEDs).
Telescopic optics, fibreoptic collection.
\subsection{The Unreasonable Effectiveness of Signal Processing}
\section{Current Research}
Guri {\it et al.} But they are covert channels. But these are covert
channels. Difference between covert channels and side channels
(ref.\ Kocher).
\subsection{Resurgence of Interest 201?--present}
Aside from the `Compromising Reflections' paper, not much happened until
around 2010, except for\ldots\footnote{Parts of this section was presented at
EMC Europe 2018, in Amsterdam, the Netherlands (\emph{International Symposium
and Exhibition on Electromagnetic Compatibility}), 27--30 August 2018
\cite{Loughry2018a}.}
\subsection{Perspective}
It's not only LEDs; and LEDs are not only used as status indicators; Figure:
\emph{all} the information channels in and out of a PC---or more accurately,
an information processing system. A new conception of control zone;
Robinson's `energy gap' concept and its applicability to crypto.
\section{Future Directions}
Unpublished research
\subsection{LED Reversing}
\subsubsection{Classical covert channels}
\subsubsection{Dead blow hammer}
\bibliographystyle{agsm}
\bibliography{consolidated_bibtex_file}
\end{document}
